---
title: "How to solve structogram using the RStudio"
author: "Shlapak Vladislav"
date: "25.12.2020"
output: powerpoint_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


## Conent

1. What is structogram
2. How we may use it
3. How do we can use Rstudio to solve it
4. Reverence

## What is structogram

Structorgram is one of type way to represent algorithms. Usually, use sctructogram
make more easy to understand what your algorithms do. 

## How we may use it

For example we may use it to solve a lot of problems. 

## How do we can use Rstudio to solve it

```{r, echo = TRUE}
newone_2 <- NULL
a <- 1
while (a <= 10){
  b = 20 - 2 * a
  if (a > b){
    newone_2 = append(newone_2, "X")
    #print ('X')
  } else {
    newone_2 <- append(newone_2, "O")
    #print ('O')
  }
  a <- a + 1
}
print (newone_2)
```

## How do we can use Rstudio to solve it
```{r echo= TRUE}
newone_4 <- NULL
a <- 10
while (a > 1){
  b <- 10
  while (b > a) {
    if (a %% 2 == 0){
      newone_4 <- append(newone_4, "A")
      #print ("A")
    }
    else {
      newone_4 <- append(newone_4, "B")
      #print ("B")
      }
    b <- b - 1
  }
  a <- a - 1
}
print (newone_4)
```

## How do we can use Rstudio to solve it
```{r, echo = TRUE}
newone_5 <- NULL
a <- 0
b <- 5
while (a < 4){
  c = b - a
  while (b > c){
    if (a %% 2 == 0){
      c = 0
    }
    else{
      c = 1
    }
    while (c < a){
      newone_5 <- append(newone_5, c)
      #print (c)
      c = c + 1
    }
    b = b - 1
  }
  a = a + 1
}
print (newone_5)
```

## Reverence
Of course you can find [my github repository](https://github.com/Wicchi/presentation_str) with all files.



